### 2020-06-17 manuscript/report_technical_appendix.Rmd
add Ehinger et al (2019) results

(@) The algorithm checks whether samples are valid: Samples for which the x- or y-coordinates are NA, infinity, or (0,0) are marked (internally) as invalid.
(@) Samples that match the blink indicator are labeled as blinks.
(@) If the unit is px, the x- and y-coordinates are transformed into va with: 
    i. The coordinates are centered ([0,0] is center)
    ii. $\theta_{deg} = atan(\frac{x*res_x}{d_{screen}*dim_x})\frac{180}{\pi}$
(@) Samples that are outside the screen are marked as invalid.
(@) Velocities and accelerations for the x- and y-coordiantes are calculated using a Savitzky-Golay filter (3rd order, length = 5).
(@) Combined velocities and accelerations are calculated as: $v = f \sqrt{v_x^2 + v_y^2}$ and $a = f \sqrt{a_x^2 + a_y^2}$ with $f$ as the sampling rate.
(@) Velocities and accelerations of value zero are nudged to be 0.01.
(@) Samples with velocity above 1000 deg/s or acceleration above 100000 deg/s$^2$ are marked as invalid.
(@) The sample-to-sample angle is calculated as: 
$$\theta_t = atan2(\frac{y_{t+1} - y_t}{x_{t+1} - x_t}) - atan2(\frac{y_t - y_{t-1}}{x_t - x_{t-1}}).$$ 
Angles are normalized to $[0,2\pi]$ by adding $2\pi$ to negative values.
(@) Samples that have an angle with value NA are marked as invalid.
(@) The velocity, acceleration, and angle of invalid samples are set to NA.

@@

(@) Relabels posterior states of samples with recursive algorithm:
    i. If a fixation or smooth pursuit sample has no previous or following sample with the same label (single sample event), 
it is relabeled as the label from the previous sample.
    ii. If a PSO sample is followed by a saccade sample or following a non-saccade sample,
it is relabeled as the last different label.
    iii. Saccade events (batch of consecutive saccade samples) below the minimum saccade duration (in s) are relabeled as the label from the previous event.
    iv. These steps are applied recursively until all conditions are met.
(@) For each event (batch of subsequent valid samples belonging to the same label), the following metrics are computed:
    i. Fixations:
        a. Duration: Max. timestamp - min. timestamp
        b. Position: Trimmed mean (20%) of x- and y-coordinates
    ii. Saccades, PSOs, and smooth pursuits:
        a. Duration: Max. timestamp - min. timestamp
        b. Start: First x- and y- coordinates
        c. End: Last x- and y- coordinates
        d. Amplitude: Euclidian distance from start to end
        e. Max. velocity
        f. Avg. velocity
        g. Max. acceleration $\cdot 1000$
        h. Avg. acceleration $\cdot 1000$
        i. Direction: $\theta = atan2(\frac{end_y - start_y}{end_x - start_x})$

>>>>

(@) The algorithm checks whether samples are valid: Samples for which the x- or y-coordinates are NA, infinity, or (0,0) are marked (internally) as invalid.
(@) Samples that match the blink indicator are labeled as blinks.
(@) If the unit is px, the x- and y-coordinates are transformed into va with: 
    i. The coordinates are centered ([0,0] is center)
    ii. $\theta_{deg} = atan(\frac{x \cdot res_x}{d_{screen} \cdot dim_x})\frac{180}{\pi}$
(@) Samples that are outside the screen are marked as invalid.
(@) Velocities and accelerations for the x- and y-coordiantes are calculated using an SG filter (3rd order, length = 5).
(@) Combined velocitiy and acceleration are calculated as: $v = f \sqrt{v_x^2 + v_y^2}$ and $a = f \sqrt{a_x^2 + a_y^2}$, with $f$ as the sampling rate. Note that acceleration is only multiplied by the sampling rate once. The second multiplication is done during postprocessing.
(@) Velocity and acceleration of value zero are nudged to be 0.01.
(@) Samples with velocity above 1000 deg/s or acceleration above 100 deg/s are marked as invalid.
(@) The sample-to-sample angle is calculated as: 
$$\theta_t = atan2(\frac{y_{t+1} - y_t}{x_{t+1} - x_t}) - atan2(\frac{y_t - y_{t-1}}{x_t - x_{t-1}}).$$ 
Angles are normalized to $[0,2\pi]$ by adding $2\pi$ to negative values.
(@) Samples that have an angle with value NA are marked as invalid.
(@) The velocity, acceleration, and angle of invalid samples are set to NA.

@@

(@) Relabels posterior states of samples with recursive algorithm:
    i. If a fixation or smooth pursuit sample has no previous or following sample with the same label (single sample event), 
it is relabeled as the label from the previous sample.
    ii. If a PSO sample is followed by a saccade sample or following a non-saccade sample,
it is relabeled as the last different label.
    iii. Saccade events (batch of consecutive saccade samples) below the minimum saccade duration (in s) are relabeled as the label from the previous event.
    iv. These steps are applied recursively until all conditions are met.
(@) For each event (batch of subsequent valid samples belonging to the same label), the following metrics are computed:
    i. Fixations:
        a. Duration: Max. timestamp - min. timestamp
        b. Position: Trimmed mean (20%) of x- and y-coordinates
    ii. Saccades, PSOs, and smooth pursuits:
        a. Duration: Max. timestamp - min. timestamp
        b. Start: First x- and y- coordinates
        c. End: Last x- and y- coordinates
        d. Amplitude: Euclidian distance from start to end
        e. Max. velocity
        f. Avg. velocity
        g. Max. acceleration $\times f$
        h. Avg. acceleration $\times f$
        i. Direction: $\theta = atan2(\frac{end_y - start_y}{end_x - start_x})$
